\subsection{Impact of using one environment \note{N}}
A pressing issue with the results presented in this report is that they are only collected from one environment. Due to limitations of the thesis only one environment has been when testing the algorithms. This presents a practical difficulty regarding the problem statement, considering that it is impossible evaluate the generality of the algorithms implemented and tested in this study. From the the results of the DBN-\etre\ algorithm there are indications that the optimizations applied to the algorithm may be the specific for the Invasive Species environment. Which reduces the creditability regarding the generality conclusions presented in this thesis. The issue presented itself in the fact there is no way within the scope of this thesis to evaluate the performance of the agent without the optimizations applied. 

Nevertheless, as discussed in section \ref{sec:e3_factored_discussion} the DBN-\etre\ algorithm converge quick to an optimal policy, which takes a considerate longer time to MBIE algorithm. Even though developed in parallel the generality of MBIE is more credible due to the fact it was simultaneously tested alongside Invasive Species in a simpler environment representing a grid world. Forcing the generality during construction of the agent. However even though the generality was partly forced during development, the lack of verification is hard to look over. 

\todo[inline]{Add connection to results, a lot better}