\section{Limitations \note{Ny Text}}
\label{sec:discuss_limitations}
In section \ref{sec:limitations}, the limitations for the project were stated and besides the fact that this thesis focuses environments with large state spaces. In order for the results from testing the algorithms selected to be relevant, the choice of environment is significant. The information gathering process during the pre-study was a more complex process than expected. The clear limitation of environment phases reduced the overall complexity with the reinforcement learning field and served as a great way to narrow the field of study. Without the reduction of the potential open research areas in reinforcement learning by first selecting the problem type and a corresponding environment the project would have become significant arduous to manage and execute. 

Nevertheless, there is also a different aspect of making an early choice of environment and problem area. The early decision of environment could possibly have eliminated algorithms from other fields in reinforcement learning which could have yielded superior results than the results collected in this project. Although, given the circumstances of the project, a delay in the choice of environment only could have lead to time spent wasted and perhaps resulted in a direction of the project not leading to any significant results at all. 

Because some papers do not include proper testing, it is possible that a algorithm only works in theory due to limitations with today computers computational power and memory. Another reason behind focusing on open research topics is on the grounds that the group lacks extensive background in the reinforcement learning field and have an desire to start working with practical issues rather than spending all the time in the beginning of the project reasoning about algorithms strength and weakness first handed. Instead focusing on combining the study of reinforcement learning in general and bringing two selected agents to life, the learning outcome has been maximized and as the project matured the knowledge and understanding of the subject also matured making it easier to reason about the qualities of the algorithms and also find areas where optimizations can be applied. 