\section{Model-based interval estimation}
\label{sec:mbie}

Model-based interval estimation is a version of value iteration whose main
feature is its use of confidence intervals for the state-action values.
Optimistic bounds to these confidence intervals are computed, by means of
finding an optimistic bound for transition probabilities. The optimistic bounds
for the transition probabilities are then used in standard value iteration to
compute state-action values, from which an optimal policy can be found. State
values are also computed at this point.

Since the confidence intervals become less wide when the the number of data
points that they are based on increases, the more times a state-action pair
has been visited, the less optimistic the bounds for these intervals will be
\parencite{dietterich2013pac}. This has the net result of promoting
exploration of state-action pairs as long as the confidence intervals are
wide, but as the state-action pairs have been tried more and more times, the
agent behaves in a less exploratory fashion. 


\begin{comment}
Model-based interval estimation is a modification of value iteration whose main feature is its  addition of confidence
intervals to the state-action values. These confidence intervals allow the agent to choose between
actions, based on how confident it is about its evaluation of them. In effect,
the less certain the agent is about its evaluation of the states and actions,
the more exploratory the actions will be. When the agent is more confident
however, it will exploit what it has learned so far about the MDP
\parencite{dietterich2013pac}.
\end{comment}

\input{algorithms/MBIE/computep.tex}
\input{algorithms/MBIE/modification_of_value_it}
\input{algorithms/MBIE/optimistic_estimations.tex}
\input{algorithms/MBIE/gt.tex}
